Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-12 WSSSPE1_report/WSSSPE1_summary_report.tex
Added affiliation information for myself
Summarizing education and training papers.

\todo{text about papers and discussion in this part of the workshop}

>>>>

The papers describing education and training were focused primarily on how
these aspects of community development impact on the long-term sustainability
of software projects.  \cite{Girotto_WSSSPE} described the impact of the
mandate within the International Centre for Theoretical Physics (ICTP) to
foster resources and competences in software development and HPC, resulting in
the development of educational curricula directed in this area.  The paper
itself described the changes made in these curricula as a result of the current
changes in the HPC and scientific software landscape due to the advent of
scripting languages, new programming paradigms and new types of hardware such
as accelerator technologies.  The development of a workshop, with carefully
selected participants and an immersive approach to learning, was identified as
a major success for educating and developing new scientific software developers
from targeted domains.

\cite{Crawford_WSSSPE} addressed education and training within computational
chemistry frameworks, particularly as these frameworks attempt to address
next-generation computer hardware and software and as chemistry courses
emphasize lab work over computational education.  The authors identify this
lack of computational awareness and training as the primary challenge to future
advances in computational chemistry.  The authors propose a new institute for
computational chemistry, emphasizing collaboration (and a licensing structure,
such as LGPL or more permissive) and education of future generations of
chemistry researchers.
